Assigning Scouts to Optimal Patrols

### 2016-06-08 draft1.tex
Added Appendix C on counting

For our problem, we let the scouts be vertices in our graph. A directed edge between Scout A and Scout B has a weight proportional to how much Scout A likes Scout B. A partition of a graph is a grouping of vertices, thus a partition of scouts is considered a troop. Whenever our graph is arranged into two partitions, we then can assess this arrangement based on a scoring criterion (or an objective function). We would like to find a partition of the vertices in the graph that either minimizes or maximizes an objective function given constraints on the sizes of subsets generated by our partition. This results in a complete, directed graph on 13 vertices having edge weights 0, 1, or -1, corresponding to indifference, approval, or disapproval, respectively. Scoutmaster Bruce specifically would like two patrols from the 13 scouts - one of size 6, the other of size 7. The total number of partitions given these constrants is $\binom{13}{6} = \binom{13}{7} = 1716$. This number is reasonable enough that we may calculate the total loss of every valid grouping and select the partition with the lowest or highest score depending on the objective function.

@@

\bibliographystyle{amsplain}
\begin{thebibliography}{10}

>>>>

For our problem, we let the scouts be vertices in our graph. A directed edge between Scout A and Scout B has a weight proportional to how much Scout A likes Scout B. A partition of a graph is a grouping of vertices, thus a partition of scouts is considered a troop. Whenever our graph is arranged into two partitions, we then can assess this arrangement based on a scoring criterion (or an objective function). We would like to find a partition of the vertices in the graph that either minimizes or maximizes an objective function given constraints on the sizes of subsets generated by our partition. This results in a complete, directed graph on 13 vertices having edge weights 0, 1, or -1, corresponding to indifference, approval, or disapproval, respectively.

Scoutmaster Bruce specifically would like two patrols from the 13 scouts - one of size 6, the other of size 7. Thus, it can be simpler to calculate all possible combinations of the scouts into groups of 
The total number of partitions given these constrants is $\binom{13}{6} = \binom{13}{7} = 1716$ (see \textit{Appendix C}). This number is reasonable enough that we may calculate the total loss of every valid grouping and select the partition with the lowest or highest score depending on the objective function.

@@

\section*{Appendix C}
Scoutmaster Gene Bruce wanted to arrange 13 scouts into two groups where one group will have 6 scouts and the other will have 7 scouts. We can find the number of combinations possible of the 13 scouts into a troop size of 6 or 7 using the binomial coefficient.

Let us first tackle a simpler problem to understand how to find the number of combinations. Suppose we have 4 people: A, B, C and D that we want to form groups of size 3 where the order of people does not matter. Then here are all the possible groups:
\begin{itemize}
	\item A,B,C	
	\item A,B,D
	\item A,C,D	
	\item B,C,D
\end{itemize}
Thus, there are 4 different combinations of grouping 4 people in a group of size 3. It would be impractical to list out all the possible combinations for larger number of people, thus we use the binomial coefficient formula \cite{F}:
\begin{gather*}
	\binom{n}{r} = \frac{n!}{r!(n-r)!}
\end{gather*}
where $n$ is the number of people and $r$ is the size of the group. For this small problem:
\begin{gather*}
	\binom{4}{3} = \frac{4!}{3!(4-3)!} = \frac{4\cdot3!}{3!1!} = 4
\end{gather*} 
Thus, we can see we arrive with the same result.

Now to address the question of arranging 13 scouts into a troop of size 6:
\begin{gather*}
	\binom{13}{6} = \frac{13!}{6!(13-6)!} = 13!/(6!7!) = 1716
\end{gather*}
The other troop would have a size of 7:
\begin{gather*}
	\binom{13}{7} = \frac{13!}{7!(13-7)!} = 13!/(7!6!) = 1716
\end{gather*}
Therefore the number of combinations possible for arranging 13 scouts into 6 or 7 troop size is 1716.
\bibliographystyle{amsplain}
\begin{thebibliography}{10}
